---
title: "p8105_hw1_hz3023"
output: github_document
date: "2025-09-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
```{r cars}
library(tidyverse)
library(moderndive)
data("early_january_weather")
Problem1 <- early_january_weather
variable.names(Problem1)
nrow(Problem1)
ncol(Problem1)
mean(Problem1$temp)

```
* There are 15 variables in this dataset. They are origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, and time_hour. 
Using nrow, we can know that there are 358 observations. Using ncol, we can know there are 15 variables.
The mean temperature in this dataset is 39.58.
***
```{r}
ggp_problem1= ggplot(Problem1, aes(x=time_hour, y=temp, color=humid))+geom_point()
ggsave("HW1P1ggp.pdf",ggp_problem1, width=8, height=6)
ggp_problem1
```

*This scatter plot shows the variation of temperature throughout January over time. The temperature fluctuates every day and there is no discernible trend. However, the temperature is generally higher during the day and lower at night. The period with higher humidity occurs more frequently in the middle of January.

## Question 2
```{r}
set.seed(1) 
RS<-rnorm(10)
LV<-RS> 0
CV<-letters[1:10]
FV<-factor(rep(c("low", "medium", "high"), length.out = 10))
Problem2<-data.frame(RS, LV, CV, FV)
mean(Problem2$RS)
mean(Problem2$LV)
mean(Problem2$CV)
mean(Problem2$FV)
```
* The mean for the random sample of size 10 from a standard normal distribution is 0.13. The mean for the logical vector is 0.6. Both character vector and factor vector don't have mean.
